### 2015-06-04 review1/response.txt

> 3. Fig.2. I propose to change color for case s3 from purple to (for example) green to distinguish results (it is hard to do now).

The colour has been changed to green.

> 4. Conclusions. When you are saying that VacTH is a promising tool for a real-feedback control, on what reasoning are you relying? In the text it is shown that VacTH is able to reconstruct plasma surface with 'reasonable' accuracy. I think in order to conclude about it's applicability for real-time control it should be verified against another real-time tools. My conclusion from the results shown is that further improvements in the code are needed to make it more robust (that is required for real-time feedback control).

The conclusion we draw in the paper is that VacTH is promising for real-time shape control. In our opinion, the accuracy of VacTH shape reconstruction shall be reasonable for real time plasma position/shape control. However, we agree that the robustness (and the accuracy as well) should be improved. There are actually new results for VacTH parameters optimizations. We do not think that VacTH must necessarily be compared to other real-time shape reconstruction tools providing that it shows enough accuracy, robustness and speed required by a particular feed-back algorithm. Since such an algorithm does not exist yet on COMPASS, we do not have absolute measures.
We have extended the last sentence of the conclusions: "We conclude that VacTH is a promising tool pertinent for a real-time feedback control of the plasma shape, although its robustness and accuracy should be improved."

Additional amendments to the manuscript:
1. VacTH reference updated in abstract to "[B. Faugeras et al., PPCF 2014, 114010]".
2. Figures in the Results chapter have been scaled down to 97 % in order to fit the longer reference list.
3. A grammatical error has been corrected: "For shot 6962, equilibria with TS pressure profiles and with linear $p'$ and $FF'$ are used." ("are used" was missing in the original text.)
4. Paragraphs are no longer used in Conclusions in order to save space.

### 2015-06-12 review1/response.txt

Dear editors, dear referee,

thank you for your valuable comments concerning our manuscript. We have addressed all of them and amended the text accordingly. Please find detailed answers below.

Best regards,
Jakub Urban et al.

@@

> 3. Fig.2. I propose to change color for case s3 from purple to (for example) green to distinguish results (it is hard to do now).

The colour has been changed to green.

> 4. Conclusions. When you are saying that VacTH is a promising tool for a real-feedback control, on what reasoning are you relying? In the text it is shown that VacTH is able to reconstruct plasma surface with 'reasonable' accuracy. I think in order to conclude about it's applicability for real-time control it should be verified against another real-time tools. My conclusion from the results shown is that further improvements in the code are needed to make it more robust (that is required for real-time feedback control).

The conclusion we draw in the paper is that VacTH is promising for real-time shape control. In our opinion, the accuracy of VacTH shape reconstruction shall be reasonable for real time plasma position/shape control. However, we agree that the robustness (and the accuracy as well) should be improved. There are actually new results for VacTH parameters optimizations. We do not think that VacTH must necessarily be compared to other real-time shape reconstruction tools providing that it shows enough accuracy, robustness and speed required by a particular feed-back algorithm. Since such an algorithm does not exist yet on COMPASS, we do not have absolute measures.
We have extended the last sentence of the conclusions: "We conclude that VacTH is a promising tool pertinent for a real-time feedback control of the plasma shape.We conclude that VacTH is a promising tool pertinent for a real-time feedback control of the plasma shape. We will further improve its robustness and accuracy and test the code within a suitable feedback algorithm."

### 2015-06-12 Conclusions.tex
slightly revised conclusion, RESPONSE SUBMITTED

Two new codes---FREEBIE and VacTH---have been successfully set up on COMPASS, which enabled to perform an extensive cross-benchmarking and validation of free-boundary equilibrium tools. We show that FREEBIE can predict equilibria that are consistent with EFIT++ reconstructions from experimental data. FREEBIE model equilibria, either with linear $p'$ and $FF'$ profiles or with pressure profiles from Thomson scattering diagnostic, then served to assess the credibility of EFIT++ reconstructions. 
Magnetic EFIT++ reconstruction with linear $p'$ and $FF'$ features a relatively good accuracy of 1 -- 2 cm in the plasma shape but introduces systematic errors both in the shape and in internal plasma parameters, such as $W$, $l_{\mathrm i}$, $\beta_{\mathrm p}$ or $q_0$. The reconstruction properties can be significantly improved by using quadratic $p'$ for elliptical and divertor plasmas, which removes the systematic error and also improves the LCFS reconstruction. EFIT++ converges in 100~\% cases in this regime.
Optimum parameters for VacTH have been estimated. In particular, the optimum number of harmonics is 4 otherwise VacTH fails to converge in many cases, even without any input error. 16 flux loops and only 8 magnetic probes must be used as VacTH input. With less flux loops or more magnetic probes the code performs significantly worse. We conclude that VacTH is a promising tool pertinent for a real-time feedback control of the plasma shape, although its robustness and accuracy should be improved.

>>>>

Two new codes---FREEBIE and VacTH---have been successfully set up on COMPASS, which enabled to perform an extensive cross-benchmarking and validation of free-boundary equilibrium tools. We show that FREEBIE can predict equilibria that are consistent with EFIT++ reconstructions from experimental data. FREEBIE model equilibria, either with linear $p'$ and $FF'$ profiles or with pressure profiles from Thomson scattering diagnostic, then served to assess the credibility of EFIT++ reconstructions. 
Magnetic EFIT++ reconstruction with linear $p'$ and $FF'$ features a relatively good accuracy of 1 -- 2 cm in the plasma shape but introduces systematic errors both in the shape and in internal plasma parameters, such as $W$, $l_{\mathrm i}$, $\beta_{\mathrm p}$ or $q_0$. The reconstruction properties can be significantly improved by using quadratic $p'$ for elliptical and divertor plasmas, which removes the systematic error and also improves the LCFS reconstruction. EFIT++ converges in 100~\% cases in this regime.
Optimum parameters for VacTH have been estimated. In particular, the optimum number of harmonics is 4 otherwise VacTH fails to converge in many cases, even without any input error. 16 flux loops and only 8 magnetic probes must be used as VacTH input. With less flux loops or more magnetic probes the code performs significantly worse. We conclude that VacTH is a promising tool pertinent for a real-time feedback control of the plasma shape. We will further improve its robustness and accuracy and test the code within a suitable feedback algorithm.
